Shabby Pages\thanks{Supported by Sparkfish LLC.}

### 2022-03-12 paper/shabby.tex
update references

From there, we used Python's \textit{cv2} library to convert each document's color channels to grayscale, and once color data was removed, we generated and applied an Augraphy pipeline. After augmenting the images, we fit each to a standard 8.5''x11'' Letter document at various DPI levels, cropping to fit where necessary. There were several possible resizing methods, but we opted to use one which simulates using a document scanner to capture an image. Code for all of these processes is available on GitHub.

@@

\bibitem{ref_url4}
  Denoising Dirty Documents | Kaggle, \url{https://www.kaggle.com/c/denoising-dirty-documents}

\bibitem{ref_url5}
  DocCreator, \url{https://doc-creator.labri.fr}

\bibitem{ref_url6}
  Apricot, submodular optimization for machine learning, \url{https://github.com/jmschrei/apricot}

>>>>

From there, we used Python's \textit{cv2} library ~\cite{ref_url4} to convert each document's color channels to grayscale, and once color data was removed, we generated and applied an Augraphy pipeline. After augmenting the images, we fit each to a standard 8.5''x11'' Letter document at various DPI levels, cropping to fit where necessary. There were several possible resizing methods, but we opted to use one which simulates using a document scanner to capture an image. Code for all of these processes is available on GitHub.

@@

\bibitem{ref_url4}
  OpenCV, \url{https://opencv.org}
%% \bibitem{ref_url4}
%%   Denoising Dirty Documents | Kaggle, \url{https://www.kaggle.com/c/denoising-dirty-documents}

%% \bibitem{ref_url5}
%%   DocCreator, \url{https://doc-creator.labri.fr}

%% \bibitem{ref_url6}
%%   Apricot, submodular optimization for machine learning, \url{https://github.com/jmschrei/apricot}
